\Title

### 2023-02-10 Grimaldi-etal-BiolCybernetics.tex
Methods : caption through  DeepWrite

\begin{figure}%[h!]%[ht!]
    \centering
    \includegraphics[width=\linewidth]{figures/conv_HD-SNN.pdf}
    % \includegraphics[width=\linewidth]{figures/HD-SNN.png}
    \caption{
    % \textbf{- HD-SNN illustration. From left to right:} A 3D representation of the event stream as output of the DVS. A 3D convolution is applied, on the dense representation of the input, along the $X$ and $Y$ spatial axes (defining the DVS pixel grid) and the temporal axis. There are as many kernels as the possible number of motion classes in the recording. For clarity, only $4$ kernels are illustrated and some weights are not represented in the voxel grid. For each voxel on the dense representation of the event stream as input, the output of the 3D convolution is processed by the non-linearity of the MLR model (i.e. softmax function). The output of the MLR gives a probability for each class, associated to a specific kernel, to emit an output event, or spike. With an appropriate spiking mechanism, here a winner-takes-all, we obtain, as output of the HD-SNN model, a new spike train with the different spikes associated to a specific motion class. }
    \textbf{Application of HD-SNN to the motion detection task.} \textit{(Left)}~We plot here as  a raster plot a slice of the input event stream (showing ON spikes in red and OFF spikes in blue for each vertical position and time for one given horizontal position in the middle of the sensor), displaying a pure translation motion upwards. A spatio-temporal convolution is applied on the dense representation of the input, along the $X$ and $Y$ spatial axes (defining the DVS pixel grid) and the temporal axis, and summed over the two polarities. At any given time (represented by the blue dot), we show the extent of the kernels (green dashed frame). \textit{(Middle)}~There are as many kernels as the possible number of motion classes in the recording and we show the activation resulting from the convolution for this specific motion upwards. The activation can be above chance (warm colors) or below chance (cold colors). For each voxel on the dense representation of the event stream as input, the output of the 3D convolution is processed by the non-linearity of the MLR model (i.e. softmax function). The output of the MLR gives a probability for each class, associated to a specific kernel. \textit{(Right)}~By adding a spiking mechanism, here a winner-takes-all, we obtain as output of the HD-SNN model, a new spike train with the different spikes associated to a specific motion class (here red is associated to a motion upwards). Most of the motion is accuratly detected. }
    \label{fig:model}
\end{figure}

>>>>

\begin{figure}%[h!]%[ht!]
    \centering
    \includegraphics[width=\linewidth]{figures/conv_HD-SNN.pdf}
    % \includegraphics[width=\linewidth]{figures/HD-SNN.png}
    \caption{
    % \textbf{- HD-SNN illustration. From left to right:} A 3D representation of the event stream as output of the DVS. A 3D convolution is applied, on the dense representation of the input, along the $X$ and $Y$ spatial axes (defining the DVS pixel grid) and the temporal axis. There are as many kernels as the possible number of motion classes in the recording. For clarity, only $4$ kernels are illustrated and some weights are not represented in the voxel grid. For each voxel on the dense representation of the event stream as input, the output of the 3D convolution is processed by the non-linearity of the MLR model (i.e. softmax function). The output of the MLR gives a probability for each class, associated to a specific kernel, to emit an output event, or spike. With an appropriate spiking mechanism, here a winner-takes-all, we obtain, as output of the HD-SNN model, a new spike train with the different spikes associated to a specific motion class. }
    \textbf{Applying HD-SNN to the task of motion detection.} \textit{(Left)}~We plot here as a raster plot a slice of the input event stream (showing ON spikes in red and OFF spikes in blue for each vertical position and time for a given horizontal position at the center of the sensor), with a pure translation motion upwards. A spatio-temporal convolution is applied to the dense representation of the input, along the $X$ and $Y$ spatial axes (defining the DVS pixel grid) and the temporal axis. The convolution is summed over the two polarities. At any given time (represented by the blue point), we show the extent of the kernels (green dashed frame). \textit{(Middle)}~There are as many kernels as there are possible motion classes in the recording, and we show the activation resulting from the convolution for this particular motion. The activation can be above chance (warm colors) or below chance (cold colors). For each voxel on the dense representation of the event stream as input, the output of the 3D convolution is processed by the nonlinearity of the MLR model (i.e., the softmax function). The output of the MLR gives a probability for each class associated with a particular kernel. \textit{(Right)}~By adding a spiking mechanism, here a winner-takes-all associated to a thresholding, we obtain as output of the HD-SNN model a new spike train with the different spikes associated to a specific motion class (here red is associated to an upward motion). Most of the motion is detected accurately. }
    \label{fig:model}
\end{figure}
